---
title: "Figure 4"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(Racmacs)
library(r3js)
```

```{r}
plot_lndscp_data <- function(file) {
  
  lndscp_data <- readRDS(file)
  do.call(r3js, lndscp_data)
  
}
```

Legend {.sidebar}
=====================================
<font size="2">
**Fig. 4: Antibody landscapes for each serum group.** Colored surfaces show the GMT antibody landscapes for the different serum groups, light gray surfaces show the landscapes for individual sera. Gray impulses show the height of the GMT for a specific variant, after accounting for individual effects as described in Materials and Methods (which would otherwise bias the GMT for variants not titrated against all sera). The base x-y plane corresponds to the antigenic map shown in Fig. 3. The vertical z-axis in each plot corresponds to the titer on the log2 scale, each two-fold increment is marked, starting from a titer of 20, one unit above the map surface. The gray horizontal plane indicates the height of a titer of 50, as a reference for judging the landscapes against various estimates of neutralizing antibody correlates of protection. The number of sera included for the calculation of the landscapes are A) D614G sera (n=15), B) B.1.1.7 sera (n=14), C) B.1.351 sera (n=19), D) P.1 sera (n=17), E) B.1.617.2 sera (n=29), F) B.1.526+E484K sera (n=8), G) B.1.637 sera (n=3), H) C.37 sera (n=10), I) BA.1 sera (n=4), J) BA.2 sera (n=1), K) 4 weeks post 2x mRNA-1273 sera (n=67), L) >3 months post 2x mRNA-1273 sera (n=16), M) 4 weeks post 3x mRNA-1273 sera (n=26), N) >3 months post 3x mRNA-1273 sera (n=13), O) 4 weeks post 2x mRNA-1273.351 sera (n=9).
</font>

A
=====================================
### D614G sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/D614G.rds")
```

B
=====================================
### B.1.1.7 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/B.1.1.7.rds")
```

C
=====================================
### B.1.351 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/B.1.351.rds")
```

D
=====================================
### P.1 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/P.1.rds")
```

E
=====================================
### B.1.617.2 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/B.1.617.2.rds")
```

F
=====================================
### B.1.526+E484K sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/B.1.526+E484K.rds")
```

G
=====================================
### B.1.637 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/B.1.637.rds")
```

H
=====================================
### C.37 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/C.37.rds")
```

I
=====================================
### BA.1 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/BA.1.rds")
```

J
=====================================
### BA.2 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/BA.2.rds")
```

K
=====================================
### 4 weeks post 2x mRNA-1273 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/2x mRNA-1273.rds")
```

L
=====================================
### >3 months post 2x mRNA-1273 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/3x mRNA-1273 BD01.rds")
```

M
=====================================
### 4 weeks post 3x mRNA-1273 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/3x mRNA-1273 BD29.rds")
```

N
=====================================
### >3 months post 3x mRNA-1273 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/3x mRNA-1273 (6 month).rds")
```

O
=====================================
### 4 weeks post 2x mRNA-1273.351 sera
```{r}
plot_lndscp_data("../../figures/main/lndscps/2x mRNA-1273.351.rds")
```



